Building the Million Transcriptome Ocular Meta-Atlas

### 2021-03-22 manuscript_00.Rmd
vinay fixes for PR AUC

# cell type prediction
load('~/data/scEiaD/predictions_n_features-5000__transform-counts__partition-universe__covariate-batch__method-scVIprojectionSO__dims-8__preFilter.scEiaD__dist-0.1__neighbors-50.Rdata')
# test_predictions <- data.table::fread('~/data/scEiaD/390498_CTpredictortest_data_probabilities.csv.gz') %>% as_tibble %>% 
#   mutate(max_pred_prob = rowMaxs(.[,-(33:36)] %>% as.matrix ), 
#          pred_correct = ifelse(cell_type_id == true_cell_id, 'Correct', 'incorrect'))
test_predictions <- model_out$test_dat %>% as_tibble %>% 
  mutate(max_pred_prob = rowMaxs(.[,-(31:34)] %>% as.matrix), 
         pred_correct = ifelse(CellTypeID == true_label_id, 'Correct', 'incorrect'))
# created by running 'source' on src/make_dotplot_markers.R
load('~/data/scEiaD/top_markers.Rdata')
load('~/data/scEiaD/top_marker_pmid.Rdata')

>>>>

# cell type prediction
load('~/data/scEiaD/predictions_n_features-5000__transform-counts__partition-universe__covariate-batch__method-scVIprojectionSO__dims-8__preFilter.scEiaD__dist-0.1__neighbors-50.Rdata')

test_predictions <- model_out$test_dat %>% as_tibble %>% 
  mutate(max_pred_prob = rowMaxs(.[,-(31:34)] %>% as.matrix), 
         pred_correct = ifelse(CellTypeID == true_label_id, 'Correct', 'incorrect'))
# created by running 'source' on src/make_dotplot_markers.R
load('~/data/scEiaD/top_markers.Rdata')
load('~/data/scEiaD/top_marker_pmid.Rdata')
